Improvement of crash forces in structures using optimization tools.

### 2016-07-26 paper.tex
Avances

\author{L. E. Romera, M. Costas, J. Paz, J. D\'iaz, S. Hern\'andez}

\address{Structural Mechanics Group, Universidade da Coru\~na, Spain}

@@

\begin{abstract}
This investigation constitutes the continuation of a previous experimental study by the authors on the axial crushing of aluminum extrusions filled with PET foam and a GFRP skeleton. Herein, a finite element model was calibrated with the results obtained in a material testing campaign using appropriate constitutive equations. Customary models were used for the material behavior of the aluminum alloy (a J2--plasticity model) and the PET foam (Deshpande and Fleck's model). Regarding the short-fibers GFRP, a Voce plasticity model was preferred to usual viscoelastic models for simplicity, as long as the results were satisfying. After a successful validation of the finite element model, the filled aluminum extrusion was subjected to a structural optimization to achieve the best crash performance. Three relevant design variables were selected: the thickness of the outer aluminum cylinder, the thickness of the GFRP and the density of the PET foam, the latter being related to its crushing strength. Given the high computational cost of each finite element model, a multi-adaptive regression splines metamodel was fitted to a large-scale sampling. Optimum pairs were obtained for the absorbed energy, the specific energy absorption, the peak load and the component's mass; stating the relative contribution of each design variable to the crashworthiness of the crash box and enabling the choice of a balanced optimum design.
\end{abstract}\\
\emph{Keywords: blabla, blabla, blabla.}

>>>>

\author{L. E. Romera, M. Costas, J. Paz, J. D\'iaz, S. Hern\'andez.}

\address{Structural Mechanics Group, Universidade da Coru\~na, Spain.}

@@

\begin{abstract}
This work describes an investigation on the structural optimization of the crash response of two structural models: a car model and an airplane fuselage model, where the force pulse due to frontal impact or hard landing wanted to be kept as stable as possible while reducing the mass of the energy absorbing systems.  The objective functions were the variance of the force-time curves produced in the impact tests and the mass of the vehicles, both of them being minimized in a multi-objective approach using metamodeling on FE models and genetic evolutionary algorithms. Finite element models were subjected to a frontal impact test against a simplified rigid wall in the case of the car model, or to hardlanding impact for the fuselage model. Force-time curves was obtained from the analysis and suitably filtered. The objective functions were calculated as the variance of this force-time curves and the total structural mass. The objective was to obtain a force-time curve which was as close as possible to the ideal dissipator curve, with lower values of the peaks of acceleration experienced by the occupants; and to minimize the mass for fuel saving and environmental reasons. To that end, optimization strategies were planned carefully to deal with problems which are typical in crashworthiness optimization like expensive computation times and numerical noise.
\end{abstract}\\
\emph{Keywords: crashworthiness, injuries reduction, size optimization, surrogate models.}
